\documentclass{article}
\usepackage{hyperref}
\usepackage{tabularray}
\usepackage{amssymb}
\usepackage{graphicx} % Required for inserting images

\title{Retrospective}
\author{Automatic Project Detection And Tooling For Devs}
\date{}

\begin{document}
\maketitle

\section*{Answers from group members} %@Barball

\subsection*{Keep}
\begin{itemize}
  \item[\textbf{K1}] \textit{Weekly standup meetings between the team members} -- We held a meeting once per week where every team member was present at a time best for everyone. Here we discussed potential issues that we've ran into and may need help with. This was our primary method for distributing tasks, beside the issue board.
  \item[\textbf{K2}] \textit{Well established issue board and milestone system} -- The priority of issues were clear due to our extensive use of GitHub's milestone feature and issue board. High priority tasks were always solved before low priority ones, which meant we could stay ahead of the deadlines.
  \item[\textbf{K3}] \textit{Fast, asynchronous communication methods} -- Communications outside of meetings through social media. We responded quickly to the requests of other team members and could even leave messages for the others to see if they weren't available.
  \item[\textbf{K4}] \textit{Balanced division of labour} -- Our work distribution was even between team members. Noone was overworked or underworked and nobody had to stress under deadlines. We didn't allow anyone in the team to take up more work than they could handle, which lead to a healthy work-study balance.
\end{itemize}

\subsection*{Drop}
\begin{itemize}
  \item[\textbf{D1}] \textit{Multiplatfrom communication} -- Our communication was scattered across multiple platforms. Frequently we missed memos, because one member messaged another member on a platform they don't frequently check. This led to some miscommunication and a few delays.
  \item[\textbf{D2}] \textit{Retroactive discovery of issues} -- Issues were occasionally discovered after they were merged into main. We later started inspecting commits more thoroughly, which certainly helped.
  \item[\textbf{D3}] \textit{Slow communication with coach} -- Meeting times with the coach were at inconvenient times for most people, which led to difficulties when figuring out key details in the requirements.
\end{itemize}

\subsection*{Improve}
\begin{itemize}
  \item[\textbf{I1}] \textit{Non-descriptive issue specifications} -- Especially early on, figuring out what key functions were supposed to do with minimal specifications was difficult. Occasionally the type signatures in issues differed from the ones we discussed on other platforms which lead to some major confusion.
  \item[\textbf{I2}] \textit{Low priority for documentation} -- Documenting code was a low priority task and was shelved in favour of adding features. We would later regret this decision, as certain larger functions became unmaintainable to anyone, but the author.
  \item[\textbf{I3}] \textit{Ad-hoc coding conventions} -- The coding style varied between team members, which makes written code easy to differentiate. We didn't use any code design principles or patterns which makes the program a bit fragile. The MVVM architechture was forced on the project which just made the codebase more complicated.
  \item[\textbf{I4}] \textit{Grammatical and linguistic shortcomings} -- English is not the first language of any of the team members, which lead to grammar that was rough around the edges. This is more noticable in the earlier documents and writeups.
\end{itemize}

\newpage
\section*{Votes}

\begin{center}
  \begin{tblr}{colspec={lccccc},hlines, vlines}
    Answer & Csüllög Benedek & Laczkó Zsófia & Petes Márton & Merth Borbála & Gergely Dániel \\
    \textbf{K1} & \checkmark & & & & \checkmark \\
    \textbf{K2} & \checkmark & & \checkmark & \checkmark & \\
    \textbf{K3} & \checkmark & \checkmark & & \checkmark & \checkmark \\
    \textbf{K4} & & \checkmark & \checkmark & \checkmark & \checkmark \\
    \hline[2pt]
    \textbf{D1} & & \checkmark & \checkmark & \checkmark & \checkmark \\
    \textbf{D2} & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
    \textbf{D3} & & \checkmark & & \checkmark & \\
    \hline[2pt]
    \textbf{I1} & & \checkmark & \checkmark & & \checkmark \\
    \textbf{I2} & \checkmark & & & \checkmark & \\
    \textbf{I3} & \checkmark & & \checkmark & \checkmark & \checkmark \\
    \textbf{I4} & & & \checkmark & & \\
  \end{tblr}
\end{center}

\section*{Answers sorted based on votes}

\subsection*{Keep}
\begin{itemize}
  \item[\textbf{K4}] Balanced division of labour
  \item[\textbf{K3}] Fast, asynchronous communication methods
  \item[\textbf{K2}] Well established issue board and milestone system
  \item[\textbf{K1}] Weekly standup meetings between the team members
\end{itemize}

\subsection*{Drop}
\begin{itemize}
  \item[\textbf{D2}] Retroactive discovery of issues
  \item[\textbf{D1}] Multiplatfrom communication
  \item[\textbf{D3}] Slow communication with coach
\end{itemize}

\subsection*{Improve}
\begin{itemize}
  \item[\textbf{I3}] Ad-hoc coding conventions
  \item[\textbf{I1}] Non-descriptive issue specifications
  \item[\textbf{I2}] Low priority for documentation
  \item[\textbf{I4}] Grammatical and linguistic shortcomings
\end{itemize}

\end{document}
